\chapter{Preface}

\section{Abstract}
Z64C is a free and open-source chess program written in \texttt{C99}. Rather
than using proven techniques in the field of computer chess, such alpha-beta
pruning or carefully hand-crafted evaluation function, this program uses MCTS
and ANN; in this sense it is similar to the popular LC0 program. The
similarities are, however, only superficial:

\begin{enumerate}
\item LC0 is based on the AlphaGoZero architecture from Google's Deepmind team;
Z64C doesn't.
\item LC0 makes use of traditional CNN as evaluation function while Z64C has
more performant heuristics.
\item More generally, Z64C happens to borrow some architecture choices from AZ
but is a separate chess program; LC0 is a reverse engineering attemp.
\item LC0 heuristics are trained from millions of games played; Z64C is designed
to converge extremely fast, even at the cost of a lower performance.
\item Z64C makes an attempt at being portable and light on system resources,
compromising on playing strenght if necessary.
\end{enumerate}

With these points, I believe I have proven my point of Z64C being a strong chess
engine, original work, for constrained systems.

\section{Features}

\section{Credits}

\section{Legal notes}

Z64C is free software: you can redistribute it and/or modify
it under the terms of the GNU AGPL
License 3.0 as published by
the Free Software Foundation. Z64C is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details. You should have received a copy of the GNU AGPL License
along with Z64C.  If not, see \url{https://www.gnu.org/licenses/agpl.txt}.

\section{Third party licenses}

\begin{leftbar}
\noindent \uline{\url{https://github.com/Cyan4973/xxHash}}
\begin{verbatim}
xxHash Library
Copyright (c) 2012-2014, Yann Collet
All rights reserved.
\end{verbatim}
\end{leftbar}

Redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met:

\begin{enumerate}
\item Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.
\item Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.
\end{enumerate}

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR
ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON
ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\begin{leftbar}
\noindent \uline{\url{https://github.com/catchorg/Catch2}}
\begin{verbatim}
Boost Software License - Version 1.0 - August 17th, 2003
\end{verbatim}
\end{leftbar}

Permission is hereby granted, free of charge, to any person or organization
obtaining a copy of the software and accompanying documentation covered by
this license (the "Software") to use, reproduce, display, distribute,
execute, and transmit the Software, and to prepare derivative works of the
Software, and to permit third-parties to whom the Software is furnished to
do so, all subject to the following: \\

\begin{addmargin}[1em]{2em}
\emph{
The copyright notices in the Software and this entire statement, including
the above license grant, this restriction and the following disclaimer,
must be included in all copies of the Software, in whole or in part, and
all derivative works of the Software, unless such copies or derivative
works are solely in the form of machine-executable object code generated by
a source language processor. \\
}
\end{addmargin}

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE, TITLE AND NON-INFRINGEMENT. IN NO EVENT
SHALL THE COPYRIGHT HOLDERS OR ANYONE DISTRIBUTING THE SOFTWARE BE LIABLE
FOR ANY DAMAGES OR OTHER LIABILITY, WHETHER IN CONTRACT, TORT OR OTHERWISE,
ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER
DEALINGS IN THE SOFTWARE.
